Paradigms in Physics 2.0

### 2017-06-09 paper.tex
tweak schedule figure
more tweaks to schedule figure
drafty conclustion

@@

\begin{figure}
\includegraphics[width=\columnwidth]{schedule}
\caption{Figure captions appear below the figure while table captions appear above the table.\label{fig1}}
\end{figure}

@@

\section{Conclusions}
This template was newly updated for the 2016 PERC Proceedings.  The
editors apologize if any errors exist, and encourage you to contact
them with changes and other suggestions.

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{schedule}
\caption{Hypothetical student schedule for a student entering without
  calculus.  Students with AP Calculus can take the junior-year
  courses one year earlier, and students who start calculus-based
  physics in the Fall of their second year are not
  delayed.\label{schedule}}
\end{figure*}

@@

@@

\section{Conclusions}
\emph{We made some changes, and the process went well.}
